Results

### 2023-02-23 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
described new model

To investigate, which variables can predict individual SVs of ER strategies, a multilevel model approach was chosen.
The ICC of the null model was $ICC=$ `r papaja::printnum(ICC_between_MLM_0)`, indicating that level-2 predictor subject accounted for `r papaja::printnum(round(ICC_between_MLM_0*100, digits = 1))` percent of total variance.
The preregistered model

>>>>

To investigate, which variables can predict individual SVs of ER strategies, a multilevel model approach was chosen.
The ICC of the null model was $ICC=$ `r papaja::printnum(ICC_between_MLM_0)`, indicating that level-2 predictor subject accounted for `r papaja::printnum(round(ICC_between_MLM_0*100, digits = 1))` percent of total variance.
The preregistered model showed a correlation of $r=$ `r papaja::printnum(attr(summary(MLM_1)$varcor[1]$ID,"correlation")[1,2])` of the random effects subjects and recoded strategy.
In addition with the estimation that our model explained `r papaja::printnum(MLM1_r2[2])` percent of variance, we assumed our model was overfitted due to inclueding recoded strategy as random slope.
We therefore set a new model without the recoded strategy as random slope factor, that follew the specification:

$$
\begin{split}
SV \sim \text{effort rating} + \text{arousal rating} + \text{utility rating} + corrugator \text{ activity} \\\ + levator \text{ activity} + (1 |subject)
\end{split}
$$
